\tool

### 2018-04-03 paper/paper.tex
Reading group 4/3

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.

@@

To determine if an error was fixed, we take several things into consideration: First, our approach ignores errors that are reported as fixed but were not located in files modified by the developer. This ensures that the GitHub user will be familiar with the code change and error fix. Second, we ignore instances where only delete actions were detected between the base and head versions of a file. This avoids making recommendations in situations where bugs are removed but not fixed. For example, a refactoring task such as renaming a class is presented in the GitHub diff as removing code from the original file. This can eliminate bugs reported by Error Prone between code versions, but may also just move the error to another location in the source code. Similarly, we also ignore deprecated classes because the error reported was not fixed. These conditions help us minimize the number of false positives and prevent errant recommendations in our approach.

@@

We used real-world open source software applications to evaluate \tool. To choose study projects from the millions of GitHub repositories, we selected projects that met the following criteria:

\begin{itemize}
\item primariy written in Java,
\item build using Maven,
\item do not already use \textsc{Error Prone},
\item ranked among the top starred repositories
\end{itemize}

Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code. To determine if a repository was a Maven project, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory. We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin. Our approach targets projects that don't use \textsc{Error Prone} to recommend the tool to developers who are less likely to be knowledgeable about the tool. We chose the most starred repositories to study the most popular projects on GitHub. Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.

To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence. This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars. For filtering of repositories, we sorted the top 100 projects by the most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

We designed our evaluation to gather quantitative and qualitative data addressing our research questions.  To analyze 700+ repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs with \tool~running on multiple virtual machines.

@@

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer. If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change. Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation. In situations where one commit or pull request provided multiple opportunities for a recommendation, the authors would examine the changes and select one of the errors reported as fixed to recommend \textsc{Error Prone} to the developer.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the total number of new pull requests and commits, and compared it to the amount recommendations made by our tool. We calculated the rate of true positive recommendations during the span of our study to measure the recommendation rate for each GitHub repository used in our evaluation. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.

@@

For our second research question, we accumulated responses from developers in our follow-up survey presented in recommendations from \tool~and by email to determine the usefulness of our system. We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks. An optional free response section was provided at the end for respondents to describe explain why or why not they found the recommendation useful. These responses were used to analyze developers' reactions to our automated recommendation. Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our approach based on feedback from software developers.

>>>>

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work. This also allows our system to easily be integrated into continuous integration builds for software applications to analyze code and recommend development tools to software engineers.

@@

To determine if an error was fixed, we take several things into consideration: First, our approach ignores errors that are reported as fixed but were not located in files modified by the developer. This ensures that the GitHub user will be familiar with the code change and error fix. Second, we ignore instances where only delete actions were detected between the base and head versions of a file. This avoids making recommendations in situations where bugs are removed but not fixed. For example, a refactoring task such as renaming a class is presented in the GitHub diff as removing code from the original file. This can eliminate bugs reported by Error Prone between code versions, but may also just move the error to another location in the source code. Similarly, we also ignore deprecated classes because the error reported was not fixed. These conditions help us minimize the number of false positives and prevent errant recommendations to developers in our approach.

@@

We used real-world open source software applications to evaluate \tool. To choose projects for this study from the millions of GitHub repositories online, we used the following criteria:

\begin{itemize}
\item primariy written in Java,
\item build using Maven,
\item do not already use \textsc{Error Prone},
\item ranked among the most popular and most recently updated repositories
\end{itemize}

Our evaluation was limited to Java projects since \textsc{Error Prone} can only analyze Java source code. To determine if a repository used Maven as a build system, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory. We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin to avoid projects that already use \textsc{Error Prone}. We selected projects that don't use \textsc{Error Prone} to increase awareness of the tool in recommendations. Developers are less likely to know about the tool if the projects they contribute to do not implement it in their build.

To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence. We chose the most starred repositories to study the most popular projects on GitHub. Stars are a social aspect of GitHub where users can indicate their favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}. Using Fibonacci numbers allowed us to get a higher concentration of projects with a lower amount of stars, while fewer projects will have a very large number of stars. To filter of repositories, we grouped projects with 1 or 2 stars, 2 or 3 stars, between 3 and 5 stars, between 5 and 8 stars, etc., and sorted the top 100 projects in each group by when they were most recently updated. After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

We designed our evaluation to gather quantitative and qualitative data addressing our research questions.

\subsubsection{Setup}

To analyze 700+ GitHub repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs running \tool~on multiple virtual machines.

@@

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determines whether it is an appropriate case to make a recommendation to the developer. For this study, we streamlined this process to send an email for the authors to review if a recommendation was proposed by our system. After the authors reviewed the code changes, if we deemed it was a true positive case we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on the pull request or commit. Otherwise, we noted the instance of a false positive in our approach and did not make the recommendation. In situations where one repository code change provided multiple opportunities for a recommendation, the authors examined each of the changes and selected one of the errors reported as fixed to recommend to the developer.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the total number of new pull requests and commits, and compared it to the amount recommendations made by our tool. We calculated the rate of true positive recommendations during the span of our study to measure the recommendation rate for each GitHub repository used in our evaluation. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by the authors to the total number of instances where a recommendation reported by \tool.

@@

For our second research question, we accumulated responses from developers in our follow-up survey presented in recommendations from \tool~and by email to determine the usefulness of our system. We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks. An optional free response section was provided at the end for respondents to describe explain why or why not they found the recommendation useful. These responses were used to analyze developers' reactions to our automated recommendation. Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our approach based on feedback from software developers. We measured the response rate by observing the total number of recommendations made, the total number of survey responses, and the positive and negative responses from developers who received a recommendation via \tool~and via email.
